The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2020-09-01 Writeup/manuscript.tex
updated results

A subset of the SSVEP data was previously published as part of an earlier demonstration of parametric responses to rotation symmetry in wallpaper groups \cite{RN1725}. We replicate that result using our Bayesian approach, and find the same parametric effect in the psychophysical data (Supplementary Figure 4.1 - NEEDS TO BE LABELED IN THE SM). We also conducted analyses looking for effects of index and normality in our two datasets.

We conclude that the hierarchy of complexity among wallpaper groups is reflected in precise detail in both brain responses and performance in a psychophysical task.

>>>>

SSVEP data from four of the wallpaper groups (P2, P3, P4 and P6) was previously published as part of our earlier demonstration of parametric responses to rotation symmetry in wallpaper groups\cite{RN1725}. We replicate that result using our Bayesian approach, and find the same parametric effect in the psychophysical data (Supplementary Figure 4.1 - NEEDS TO BE LABELED IN THE SM). We also conducted analyses looking for effects of index and normality in our two datasets, and found that ... Finally, we conducted a correlation analysis comparing SSVEP and behavioral data, and found a small ($R^2 = 0.44$) but above-zero correlation, as indicated by our confidence intervals. There are several factors that might explain the relatively weak correlation, most prominently the fact that the same individuals did not participate in each of the two experiments. Nevertheless, we find the relationship between the two datasets interesting, because it suggests that our psychophysical and SSVEP measurements are tapping into the same underlying mechanisms.
